A cautionary note on the use of Ornstein Uhlenbeck and other models in macroevolutionary studies

### 2015-04-29 Manuscript/ohyou_SuppInfo.tex
Renamed supp mat file

\section{Supplementary Material}
\setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}}

  \subsection{Literature review}
    To get an overview of the use of OU models in ecology, evolution and palaeontology, we used Google Scholar (accessed 13th March 2015) to locate papers published between 2005 \citep[when the R package ouch was released;][]{Butler:2004aa} and 2014 that contained the terms ``Ornstein Uhlenbeck'' and either ``'ecology'', or ``evolution'' and ``biology'' (the ``biology'' term was added to omit physics papers which also use the term ``evolution''), or ``paleo/palaeo''. 
    We also recorded the total number of papers containing the terms ``ecology'', or ``evolution'' and ``biology'', or ``paleo/palaeo'', published between 2005 and 2014 and plotted the number of OU papers published each year as a proportion of the total number of papers published (Fig. \ref{figure.literature}).

@@

    For each of these papers we recorded the number of species in the analysis, the study group (amphibians, birds, fish, mammals, reptiles, invertebrates or plants), the statistical package or specific R package used to fit the models, and the reason the authors state for using an OU model (ancestral state reconstructions, detecting convergent evolution, controlling for phylogeny, selecting a model of trait evolution, or other). 
    Where papers included multiple analyses using different numbers of species we used the median number of taxa. 
    Where papers had multiple study groups, statistics/R packages or reasons for fitting OU models we counted them in each relevant category. 
    We summarise these results in Figures 1 and 2 and Table 1, and the full dataset is available below along with the full list of references.

    In total, our literature search found 3720 papers published between 2005 and 2014, and the number has increased substantially since 2005 (Fig. 1). 
    Most papers fit OU models to phylogenies with fewer than 100 taxa (mean = 166.97 $\pm$ 43.86, median = 58, Figure 2 and Table S1). 
    The majority of papers fit OU models using R packages, particularly GEIGER and, although other uses are becoming more common, most papers use OU models in an effort to discern the ``best'' model of trait evolution or to control for phylogenetic non-independence (Table S1).

@@

@@

>>>>

\documentclass[a4paper,12pt]{article}

\usepackage[osf]{mathpazo} % palatino
\usepackage{ms}            % load the template
\usepackage[round]{natbib} % author-year citations
\usepackage{graphicx}
\usepackage{parskip} 
\usepackage{enumerate} 
\usepackage{longtable}
\usepackage{pdflscape}
\usepackage{fullpage}
\usepackage{hyperref}
\usepackage[nomarkers, nolists]{endfloat}  % To push floats to the end   
\pagenumbering{arabic}

\begin{document}

\raggedright
\doublespacing
\setlength{\parindent}{1cm}

\section{Supporting Information}
\setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}}

  \subsection{Literature review methods}
    To get an overview of the use of OU models in ecology, evolution and palaeontology, we used Google Scholar (accessed 13th March 2015) to locate papers published between 2005 (when the R package ouch was released; Butler and King 2004) and 2014 that contained the terms ``Ornstein Uhlenbeck'' and either ``'ecology'', or ``evolution'' and ``biology'' (the ``biology'' term was added to omit physics papers which also use the term ``evolution''), or ``paleo/palaeo''. 
    We also recorded the total number of papers containing the terms ``ecology'', or ``evolution'' and ``biology'', or ``paleo/palaeo'', published between 2005 and 2014 and plotted the number of OU papers published each year as a proportion of the total number of papers published (Fig. 1 in the main text).

@@

    For each of these papers we recorded the number of species in the analysis, the study group (amphibians, birds, fish, mammals, reptiles, invertebrates or plants), the statistical package or specific R package used to fit the models, and the reason the authors state for using an OU model (ancestral state reconstructions, detecting convergent evolution, controlling for phylogeny, selecting a model of trait evolution, or other). 
    Where papers included multiple analyses using different numbers of species we used the median number of taxa. 
    Where papers had multiple study groups, statistics/R packages or reasons for fitting OU models we counted them in each relevant category. 
    We summarise these results in Figures 1 and 2 and Table 1 in the main text, and the full dataset is available in Table \ref{table:litreview} along with the full list of references.

  \subsection{Literature review results}
    In total, our literature search found 3720 papers published between 2005 and 2014, and the number has increased substantially since 2005 (Fig. 1 in main text). 
    Most papers fit OU models to phylogenies with fewer than 100 taxa (mean = 166.97 $\pm$ 43.86, median = 58, Figure 2 in main text and Table \ref{table:litreview}). 
    The majority of papers fit OU models using R packages, particularly GEIGER and, although other uses are becoming more common, most papers use OU models in an effort to discern the ``best'' model of trait evolution or to control for phylogenetic non-independence (Table \ref{table:litreview}).

@@

\label{section:refs} 

@@

\end{document}
